Multiset-trie data structure

### 2019-03-14 tex/tex/s_intro.tex
The first version of contributions paragraph (part 3)

The existing solutions to the implementation of the containment queries include the inverted file \cite{manningBook}, signature tree \cite{} or B+ tree~\cite{Helmer2003}. These solutions provide a key-value look-up for elements of a multiset implying that containment operations are still element-wise. (? Is it possible to state more precisely the drawbacks of these solutions? ?)

@@

% 
--------------------------------------------------------------------------------------------------------------------------------------------
%
% 3rd part: contributions

Empirical studies on real data show, that multiset-trie is sensitive to the context, which can 
be further used to optimize data structure for particular data. Moreover, knowing the data 
it is possible to estimate the overall performance of the multiset-trie both time and space 
related using our mathematical theory that describes multiset-trie.
%
The comparative study shows how efficient multiset-trie is by outperforming inverted file in 
both equality and containment queries by up to 4 orders of magnitude in the time consumed by 
query.

>>>>

The existing solutions to the implementation of the containment queries include the inverted index \cite{manningBook}, signature tree \cite{} or B+ tree~\cite{Helmer2003}. These solutions provide a key-value look-up for elements of a multiset implying that containment operations are still element-wise. (? Is it possible to state more precisely the drawbacks of these solutions? ?)

@@

% 
%--------------------------------------------------------------------------------------------------------------------------------------------
%
% 3rd part: contributions
The contributions of this paper are:
\begin{itemize}
\item A novel data structure multiset-trie which can store a set of multisets using common prefixes and provide fast containment queries. 
\item A mathematical model of a general case multiset-trie that analyses its space complexity, an estimation of a sub-tree size traversed by a containment query and therefore gives insights on containment query time complexity.
\item Empirical results of multiset-trie performance depending on a multiset space parameterization.
\item A comparative study between an inverted index and multiset-trie where the later outperforms its competitor by up to 4 orders of magnitude in the time consumed by both equality and containment queries.
\item Experimental result that shows an influence of ordering in multisets on their storage and processing.
\end{itemize}
%
